---
title: "intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 7,
  warning = FALSE,
  errors = FALSE,
  messages = FALSE
)
```

## Description

`bamExtras` is an R package that contains functions and data to support
stock assessments of fish stocks in the Southeast US Atlantic using the Beaufort
Assessment Model (BAM)

## Example usage

### Load the package

First, install and load the package. 

```{r, echo=TRUE, message=FALSE}
# Install and load package
#devtools::install_github("nikolaifish/bamExtras")
library(bamExtras)
# Load dependencies
library(stringr)
```

### Work with results of BAM assessments

```{r, echo=TRUE, message=FALSE}
# see all data objects in bamExtras
# data(package="bamExtras")$result[,"Item"]
# standardize naming conventions and assign shorter name
rdat_BS <- standardize_rdat(rdat_BlackSeaBass)
rdat_RP <- standardize_rdat(rdat_RedPorgy)
```

## Plot results from one assessment

```{r}
with(rdat_BS$t.series,
     plot(year,B,type="o",col="black"))
```

## Plot results from multiple assessments

```{r}
ylim <- range(c(0,rdat_BS$t.series$B,rdat_RP$t.series$B))
with(rdat_BS$t.series,
     plot(year,B,type="o",col="black",ylim=ylim)
     )
with(rdat_RP$t.series,
     points(year,B,type="o",col="red")
     )
```
