---
title: "workWithopenMSE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{workWithopenMSE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 7,
  warning = FALSE,
  errors = FALSE,
  messages = FALSE
)
```

## Description

`bamExtras` is an R package to that contains functions and data to support
stock assessments of fish stocks in the Southeast US Atlantic using the Beaufort
Assessment Model (BAM).

A set of functions has been developed to use BAM assessment data and outputs to condition operating models that can be used with the [openMSE](https://openmse.com/) package .

## Example usage

### Load the package

First, install and load the `bamExtras` package. 

```{r, echo=TRUE, message=FALSE}
# Install and load package
#devtools::install_github("nikolaifish/bamExtras")
library(bamExtras)

# Load dependencies
library(stringr)
```

### Work with the `openMSE` package

```{r, echo=TRUE, message=FALSE}
#install.packages("openMSE")
library(openMSE)
```

### Work with results of BAM assessments

```{r, echo=TRUE, message=FALSE}
# see all data objects in bamExtras
# data(package="bamExtras")$result[,"Item"]

# standardize naming conventions and assign shorter name
rdat_RP <- standardize_rdat(rdat_RedPorgy)
```


## Build Stock and Fleet objects

```{r}
Stock_RP <- rdat_to_Stock(rdat_RP)
Fleet_RP <- rdat_to_Fleet(rdat_RP)
```

## Assemble operating model

```{r}
OM_RP <- new("OM", Stock=Stock_RP, Fleet=Fleet_RP, Obs=Precise_Unbiased, Imp=Perfect_Imp)
```

## Run basic MSE

```{r, results="hide"}
MSE_RP <- runMSE(OM_RP)
```

## Plot results

```{r}
NOAA_plot(MSE_RP)
```

